---
title: "Classification of products based on product description"
author: "Ravi Vanam"
date: "July 13, 2017"
output: html_document
---
## R Markdown
Grocery store receipts often times contain abbreviated, and even cryptic, language
representing the products that have been sold. In order to better understand the group the types
of products our users buy, design an automated process that assigns a product category to
each line-item parsed from a receipt. 

building supervised machine learning models.



##Data

This data has 4 columns
  1. id
  2. product_text
  3. retailer
  4. category

product_text and retailer are input variables and category is the target variable.

#Process:
1.	Load the data.
2.	Understood the data, Clean the data. Removed the "id" column since it's not useful for prediction.
3.	The "product_text" column has long sentences. Feature engineered and made this column in to seven columns, each column containing a word/number. So now I have 8 input features.
4.	Divide this data containing 14767 observations in to train(80%) and validation(20%) data to assess the model performance.
5.	I built Support Vector Machines(SVM) and Naïve Bayes models using training data and measured the model performance using validation data.
6.	I got better accuracy for SVM model.
7.	Now using whole labeled data as training data, trained the SVM model.
8.	Using the above model, predicted the categories on unlabeled data.

```{r}
library(caret)
setwd("H:\\WorkSpace\\Interns\\Ibotta\\ibotta_ds_intern_exercise")
ibotta_data <- read.csv("trn.csv")
data_partition <- createDataPartition(ibotta_data[,9], p = 0.8, list = FALSE)
train_data <- ibotta_data[data_partition, ]
validation_data <- ibotta_data[-data_partition, ]

unlabled_data <- read.csv("unlabled.csv")
labled_data <- read.csv("labeled2.csv")

combined_data <- read.csv("combined_data.csv")
train_new <- combined_data[1:14767,]
test_data <- combined_data[-c(1:14767),]
#write.csv(test_data, file = "test_data.csv")



```

#Support Vector Machines Model
```{r}
library(e1071)
svm.fit <- svm(category ~ ., data = train_new,kernel='linear', scale=FALSE)

preds_svm <- predict(svm.fit, newdata = validation_data[,-9])
confusionMatrix(preds_svm, validation_data$category)


preds_svm_actual <- predict(svm.fit, newdata = test_data[,-9]) 
#write.csv(as.data.frame(preds_svm_actual), file = "predicted_svm.csv")
Results_svm <- data.frame(summary(validation_data$category),summary(preds_svm),summary(preds))
Results_svm


```


#Naive Bayes Model
```{r}

library(kernlab)
library(caret)

setwd("H:\\WorkSpace\\Interns\\Ibotta\\ibotta_ds_intern_exercise")
ibotta_data2 <- read.csv("trn.csv")

data_partition2 <- createDataPartition(ibotta_data2[,9], p = 0.8, list = FALSE)
train_data <- ibotta_data2[data_partition2, ]
validation_data <- ibotta_data2[-data_partition2, ]

library(e1071)
nb_model <- naiveBayes(category ~ ., data = train_new)

preds_nb_actual <- predict(nb_model, newdata = test_data[,-9]) 
#write.csv(preds_nb_actual, file = 'preds_nb_actual.csv')


preds <- predict(nb_model, newdata = validation_data[,-9])
confusionMatrix(preds, validation_data$category)
results_nb <- data.frame(summary(validation_data$category),summary(preds))
results_nb
```

